\section{Clustering (Unsupervised Learning)}
As the examples are unlabeled, clustering relies on unsupervised machine learning. If the examples are labeled, then clustering becomes classification.

\subsection{k-Means Clustering}
\textbf{Initialization:} performance depends on the random initialization of the seeds for the centroids (Initialize randomly, run multiple times). 

\textbf{Stopping Criterion:}  When centres don’t change,  The datapoints assigned to specific cluster remain the same,  The distance of datapoints from their centre (Threshold),  Fixed number of iterations have reached.

\textbf{Standardization of Data:} Features with large values may dominate the distance value. Features with small values will have no impact in the clustering. We should normalise values.

\begin{enumerate}
	\itemsep -0.5em
  	\item We define the number of klusters $k_{c}$
  	\item Initialize the value of k cluster centres (centroids) $C_{1}. C_{2}..C_{k_{c}}$
  	\item Assignment
  		\SubItem{Find the squared Euclidean distance between the centres and all the data points}
  		\SubItem{Assign each data point to the cluster of the nearest centre.}
  	\item Update: Update the center for each cluster.
  	\item If (stoppin criterion met) \{ Stop \} else \{go to assignment\}
\end{enumerate}

\textbf{Caluclate Cluster Center}: $C_{R_y} = \frac{Sum of x coefficients}{data points}$, $C_{R_y} = \frac{Sum of y coefficients}{data points}$ 

\subsection{Evaluation: Within-cluster sum-of-squares (WCSS) }
Sum of squared distances of samples to their closest cluster centre.

\subsection{Evaluation: Silhouette Score} 
How far away the datapoints in one cluster are, from the datapoints in another cluster. Shilloute Score for point a  =$\frac{b-a}{max(a,b)}$ where a=average intra-cluster distance i.e the average distance between each point within a cluster, b=average inter-cluster distance i.e the average distance between a cluster and its nearest neighbour cluster.

